\chapter*{Acknowledgments}

I have tremendous gratitude \\
to those people, \\
numerous and innumerable, \\
who have contributed, \\
directly or in subtler ways, \\
to this work.

Some of them are listed here. \\

\textbf{To my advisor, Winston:} I remember writing to you as a sophomore in college many years ago, asking to do research in your brand new lab, which at the time was but a few months old. Back then, I had no idea what it was to do research, and I had no relevant skills or credentials to offer, only my time and my interest to learn. Over these years I have indeed learned a lot, and I will always be grateful to you for building the place where I was able to grow.

\textbf{To my thesis committee, Trish and Steven:} Thank you for your exceptionally kind guidance, support, and feedback. I always left committee meetings with you feeling more confident in myself, and more optimistic about my progress.

\textbf{To the @yfan arc of the \texttt{\#}core channel - @isac, @brochael, @shao, @gilfunk, @narley, @broham, @gmoney, @Brittany, @sherbear, @Sam Sholes, @Paul Hook, @amymeltzer39, @alice, @Luke Morina, @Courtney Johnson, and @Jess:} Thank you for those times when you patiently watched over me as I learned new lab techniques, answered my dumb questions, and generally rescued me from predicaments of my own making. It is my fondest hope that at some point during our time together, I was able to reciprocate by being even mildly helpful. Thank you most of all for commiserating with me as we struggled together through the singular challenges of research, and celebrating the equally singular triumphs.

\textbf{To the crew that moved me into 703 (and Charles, and Charlotte, and Sven, and Manolo):} Thanks for being there, and thanks for hanging out. Let's go climbing and get a beer the next time we're all around. It's been a while.

\textbf{To mom and dad, and family further away:} It was your labor that first cultivated my growth. Accomplishments in my name are as much yours as they are mine. I flourish for you.
